Testing Methodologies for Asynchronous Centralized Simulations\\

### 2020-12-02 paper/PaperDraft2.tex
Updated paper

\title{Testing Methodologies for a Multiplayer Game Protocol\\
}

@@

>>>>

\title{Testing Methodologies for Asynchronous Centralized Simulations\\
}

@@

\subsection{Trained Model Approach}

Discuss the setup for the trained model - the tools and automatic invocation

\section{Case Study}

Discuss the specificics of the game architecture here - show the actual code and frameworks
